---
title: "Group 28 CA pollution burden"
author: "Sarah Hamilton and Katherine Rosencrance"
date: "11/14/2021"
output: html_document
---

```{r setup, include=TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#Attach the necessary packages
library(tidyverse)
library(janitor)
library(here)
```

```{r}
#Read in the data and convert the column names to lower snake case using clean_names()
ces <- read_csv(here("data","ces3demographics.csv")) %>%
  clean_names()
```
```{r}
ggplot(data = ces, aes(x = white_percent, y = ces_3_0_score))+
  geom_hex()+
  labs(x = "% White", y = "CalEnviroScreen Pollution Burden Score",
       caption = "Figure 1. CalEnviroScreen pollution burden score versus percentage of population that is white. \n The percentage of the population that is white is plotted on the x axis, with the CalEnviroScreen \n pollution burden score plotted on the y axis. The color indicates the count of census tracts that \n correspond to each point, with darker shades of green indicating higher counts of census tracts.")+
  scale_fill_gradient(low = "darkseagreen1", high = "darkgreen")+
  theme_minimal()
```

# Trends Observed
**Figure 1** shows that there is a negative correlation between the percentage of white people in the population and CalEnviroScreen scores. This means that the lower the percentage of white people in a community, the higher the scores will be. High scores indicate an area with high pollution burden and a high number of characteristics in the population that may cause the pollution to be more deadly. 

# Data Citation
California Environmental Justice Alliance. 2018. CalEnviroScreen 3.0: A Tool for Advancing Environmental Justice. https://caleja.org/wp-content/uploads/2015/09/CES3.0-5.pdf (Accessed 11/11/2021)
For more background and CalEnviroScreen 3.0 maps, go to: https://oehha.ca.gov/calenviroscreen/report/calenviroscreen-30
